### 2017-11-24 Docs/Thesis/docs/chapter1.tex
up

A burstier traffic can cause packet more buffer overflows on network \cite{burstiness-queue-lenght} \cite{modelling-of-self-similar} \cite{empirical-interarrival-study}, degenerating network performance\footnote{Fuatures such as packet-trains periods and inter-packet times affect traffic burstiness}. Also, a burstier and realistic traffic will not just impact on performance, but on measurement accuracy as well \cite{legotg-paper} \cite{background-traffic-matter}. Another key question is how applications will deal with packets. It is a well-known fact that applications have a huge performance degradation processing small packets\cite{comparative-trafficgen-tools}. A realistic synthetic traffic must not have a single packet-size but must use a distribution \cite{packet-distribution-model}.

@@

Another critical point is the flow-oriented operation of SDN networks. Each new flow arriving on an SDN switch demands an extra communication load between it and the controller. This may create a bottleneck between the switch and the controller.  We also have a flow-oriented operation on SDN switches. Since its operation relies on queries on flow tables, a stress load must have the same flow properties of an actual ISP scenario.

@@

The open-source community offers a huge variety of workload generators and benchmarking tools \cite{ditg-paper}\cite{validate-trafficgen}\cite{comparative-trafficgen-tools}\cite{performance-trafficgen}. Most of these tools were built for specific purposes and goals, so each uses different methods of traffic generation.

Some traffic generator tools offer support emulation of single application workloads. But this does not correspond to real complex scenarios, with a large number of distributed hosts in an Internet Service Provider (ISP) or even a Local Area Network (LAN).

Other tools work as packet replay engines, such as TCPreplay and TCPivo. Although in that way is possible to produce a realistic workload at high rates, it comes with some issues. First, the storage space required becomes huge for long-term and high-speed traffic capture traces. Also, obtaining good traffic traces sometimes is hard, due privacy issues and fewer good sources.

Many tools support a larger set of protocols and high-performance, such Seagull and Ostinato. Others are also able to control inter-packet times and packet sizes using stochastic models, like D-ITG\cite{ditg-paper} and MoonGen. They can give a good control of the traffic and high rates. The most relevant examples of features are controlled by these tools are:

\item Throughput, the number of bytes, number of packets.

\item Protocols. Most of the tools give support to network and transport protocols. Many also offer support to Link and Application protocols;

\item Header and payload configuration. Support for header customization includes source and destination port/addresses, QoS parameters, flags, etc. Some traffic generators also allow customizing payload bytes.

\item Inter-packet times. Some tools offer a set of stochastic distributions to control inter-packet times. The user can use these stochastic functions to emulate realistic inter-arrival times.

\item On/off periods: support of packet trains periods. Many offer stochastic models to control it.

\item Sending time and start-time: the user can use these features to control flows timings.

\item Packet-size: support for different packet sizes. Some tools offer constant values or stochastic distributions to control packet sizes.

\item Paralell flows configuration.

\item Emulation of specific applications: common examples are Web server/client communication, VoIP, HTTP, FTP, p2p applications, and so on.

Since there is so many features and tools, selecting a good configuration is by itself a research project. How to use each parameter to simulate a specific scenario is a hard question \cite{legotg-paper}\cite{selfsimilar-ethernet}. It is a manual process and demands implementation of scripts or programs leveraging human (and scarce) expertise on network traffic patterns and experimental evaluation.

Some tools like Swing and Harpoon uses capture traces to set intern parameters, enabling an easier configuration. Also, Swing uses complex multi-levels models which are able to provide a high degree of realism\cite{swing-paper}. But they have their issues as well. Harpoon does not configure parameters at packet level\cite{harpoon-paper} and is not supported by newer Linux kernels, what may be a huge problem with setup and configuration. Swing\cite{swing-paper} aims to generate realistic background traffic, but do not reach high throughputs \cite{swing-paper} \cite{legotg-paper}. Due the fact that its traffic generation engine is coupled to its modeling framework, you can't opt to use a newer/faster packet generation library. The only way of replacing the traffic engine is changing and recompiling the original code. And this is a hard task.

Since synthetic traffic traces generation is mature in academia, the creation of custom network workloads through the configuration of high-throughput open-source is an affordable task. But it is not often available in an automatic way, and most of the times is a challenging question\cite{legotg-paper}, and still, requires expert knowledge. It requires time, study, and is vulnerable to human mistakes and lack of validation. Such work may require weeks to complete a realistic reproduction of a single scenario, so most of the time it is just not done. We argue that widely (i.e. affordable) existing approaches can be regarded as simplistic often point solutions to more general cases.

Also, just choosing which workload generator tool may fit better for the user needs is not a simple question. Tools like D-ITG\footnote{\href{http://traffic.comics.unina.it/software/ITG/}{http://traffic.comics.unina.it/software/ITG/}} provide support to many different stochastic functions, Ostinato\footnote{\href{http://ostinato.org/}{http://ostinato.org/}} provides a larger support for protocols, and a higher throughput for each thread\cite{comparative-trafficgen-tools}, and others like Seagull\footnote{\href{http://gull.sourceforge.net/doc/WP_Seagull_Open_Source_tool_for_IMS_testing.pdf}{http://gull.sourceforge.net/doc/WP\_Seagull\_Open\_Source\_tool\_for\_IMS\_testing.pdf}} are responsive.

@@

Our goal is to offer an easier configuration, realism than the available platforms today, at a reasonable speed. To do this, we are introducing the concept of programmability for  traffic generation. With SIMITAR, user may program its own synthetic traffic in a platform agnostic way. The intermediate layer of the figure ~\ref{fig:layer-diagram} summarize, the goal of the project in an illustrative way.

>>>>

A burstier traffic can cause packet more buffer overflows on network \cite{burstiness-queue-lenght} \cite{modelling-of-self-similar} \cite{empirical-interarrival-study}, degenerating network performance\footnote{Fuatures such as packet-trains periods and inter-packet times affect traffic burstiness}, and  measurement accuracy\cite{legotg-paper} \cite{background-traffic-matter}. Another key question is how applications will deal with packets. It is a well-known fact that applications have a huge performance degradation processing small packets\cite{comparative-trafficgen-tools}. A realistic synthetic traffic must not have a single packet-size but must use a distribution \cite{packet-distribution-model}.

@@

Another critical point is the flow-oriented operation of SDN networks. Each new flow arriving on an SDN switch demands an extra communication load between it and the controller. This may create a bottleneck between the switch and the controller.  Also the SDN switches have a flow-oriented operation. Since its operation relies on queries on flow tables, a stress load must have the same flow properties of an actual Internet Service Provider.

@@

The open-source community offers a huge variety of workload generators and benchmarking tools \cite{ditg-paper}\cite{validate-trafficgen}\cite{comparative-trafficgen-tools}\cite{performance-trafficgen}. Most of these tools were built for specific purposes and goals, so each uses different methods of traffic generation, and enable controll of different features, such as throughput (bits/bytes per second, packets per seconds), packet-sizes, protocols and header customization, payload customization, inter-packet times, On/Off periodos, start and sending time, and emulation of applications such as Web server/client communication, VoIP, HTTP, FTP, p2p applications, and many more.

Some traffic generator tools offer support emulation of single application workloads. But this does not correspond to real complex scenarios. Other tools work as packet replay engines, such as TCPreplay and TCPivo. Although in that way is possible to produce a realistic workload at high rates, it comes with some issues. First, the storage space required becomes huge for long-term and high-speed traffic capture traces. Also, obtaining good traffic traces sometimes is hard, due privacy issues and fewer good sources. Many tools support a larger set of protocols and high-performance, such Seagull and Ostinato. Others are also able to control inter-packet times and packet sizes using stochastic models, like D-ITG\cite{ditg-paper} and MoonGen.

We have available have a variety of APIs that enable creation of traffic and custom packets, wich include low-level APIs, such as Linux Socket API,  Libpcap, Libtins, DPDK, Pcapplusplus, libcrafter, impacket, scapy and many others. These APIs enable a finer controll and customization over each packet, and are used to implement traffic generators. For example, Ostinato and TCPreplay uses Libpcap, and MoonGen uses DPDK. Also, many traffic generators provides their own API, such as Ostinato Python API, D-ITG C API, and MoonGen LUA API.

%They can give a good control of the traffic and high rates. Es example of controllable features we can list:
%\begin{itemize}
%\item Throughput, the number of bytes, number of packets.
%\item Protocols. Most of the tools give support to network and transport protocols. Many also offer support to Link and Application protocols;
%\item Header and payload configuration. Support for header customization includes source and destination port/addresses, QoS parameters, flags, etc. Some traffic generators also allow customizing payload bytes.
%\item Inter-packet times. Some tools offer a set of stochastic distributions to control inter-packet times. The user can use these stochastic functions to emulate realistic inter-arrival times.
%\item On/off periods: support of packet trains periods. Many offer stochastic models to control it. 
%\item Sending time and start-time: the user can use these features to control flows timings.  
%\item Packet-size: support for different packet sizes. Some tools offer constant values or stochastic distributions to control packet sizes.
%\item Paralell flows configuration.
%\item Emulation of specific applications: common examples are 
%\end{itemize}

If the user whats to reproduce an realistic traffic scenatio, since there is so many features and tools, selecting a good configuration is by itself a complex research project. How to use each parameter to simulate a specific scenario is a hard question \cite{legotg-paper}\cite{selfsimilar-ethernet}. It is a manual process and demands implementation of scripts or programs leveraging human (and scarce) expertise on network traffic patterns and experimental evaluation. Also, having a good compromisse between quality of realism, progamming time and scalability another challange. Since this is a complex process, a simplistic and less time-expensive sollution is choosen over a a realistic and acuratter but comple and time-costly sollution.

Some sollutions exists on the open-source comunity. Some tools like Swing and Harpoon uses capture traces to set intern parameters, enabling an easier configuration. Also, Swing uses complex multi-levels models which are able to provide a high degree of realism\cite{swing-paper}. But they have their issues as well. Harpoon does not configure parameters at packet level\cite{harpoon-paper} and is not supported by newer Linux kernels, what may be a huge problem with setup and configuration. Swing\cite{swing-paper} aims to generate realistic traffic, but focous on background traffic, and high throughputs it is not a goal off the application\cite{swing-paper} \cite{legotg-paper}. Due the fact that its traffic generation engine is coupled to its modeling framework, you can't opt to use a newer/faster packet generation library. The only way of replacing the traffic engine is changing and recompiling the original code. And this is a hard task\cite{legotg-paper}.

%Since synthetic traffic traces generation is mature in academia, the creation of custom network workloads through the configuration of  open-source tools is an affordable task. But it is not often available in an automatic way, and most of the times is a challenging question\cite{legotg-paper}, and still, requires expert knowledge. It requires time, study, and is vulnerable to human mistakes and lack of validation. Such work may require weeks to complete a realistic reproduction of a single scenario, so most of the time it is just not done. We argue that widely (i.e. affordable) existing approaches can be regarded as simplistic often point solutions to more general cases.

% Also, just choosing which workload generator tool may fit better for the user needs is not a simple question. Tools like D-ITG\footnote{\href{http://traffic.comics.unina.it/software/ITG/}{http://traffic.comics.unina.it/software/ITG/}} provide support to many different stochastic functions, Ostinato\footnote{\href{http://ostinato.org/}{http://ostinato.org/}} provides a larger support for protocols, and a higher throughput for each thread\cite{comparative-trafficgen-tools}, and others like Seagull\footnote{\href{http://gull.sourceforge.net/doc/WP_Seagull_Open_Source_tool_for_IMS_testing.pdf}{http://gull.sourceforge.net/doc/WP\_Seagull\_Open\_Source\_tool\_for\_IMS\_testing.pdf}} are responsive.

@@

Our goal is to offer an easier configuration, with a reasoble degree of realism than the available platforms today, at a reasonable speed. To do this, we are introducing the concept of programmability for  traffic generation. With SIMITAR, user may program its own synthetic traffic in a platform agnostic way. The intermediate layer of the figure ~\ref{fig:layer-diagram} summarize, the goal of the project in an illustrative way.
